\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage{fullpage}

\title{Terms of Agreement}
\date{\today}
\author{Between: Jens Christensen, Jonas Brandvik, \\ 
	Oliver Carlsson, Viktor Alexander Jakobsson}

\begin{document}
\maketitle

\begin{center}
	\begin{tabular}{ | p{3cm} | p{2.5cm} | p{5cm} | p{2cm} | p{2cm} | }
	\hline
	Name & Telephone & Email & Time disposal ambition & Grade ambition \\ \hline
	Jens Christensen & 0735-343 360 & jens.christensen@fripost.org & VM & VG \\ \hline
	Jonas Brandvik & 0705-083 060 & temberbain@gmail.com & VM & VG \\ \hline
	Oliver Carlsson & 0708-299 606 & olivercarlsson89@gmail.com & M & 5 \\ \hline
	Viktor Alexander Jakobsson & na & jakobssv@student.chalmers.se & na & na \\ \hline
	\end{tabular}
\end{center}


\section*{General}
Team leader: Jens Christensen \\
Decisive vote: Jens Christensen \\

\section*{Meetings}
\begin{itemize}

	\item Location: Is decided on previous meeting.
	\item Time: Every Monday at 10:00 am if nothing else is said.
	\item Agenda preperator: Jens Christensen
	\item Attendance: Mandatory
	\item Violation of attendance rule (more than 10 min late): Three strikes, imply bringing coffee to the next meeting.
\end{itemize}


\section*{Division of labor}
\begin{itemize}
	\item Field of responsibillities: Decided every Monday.
	\item Subtargets and Deadlines: Decided on meetings.

\end{itemize}

\section*{Decision making}
\begin{itemize}
	\item Decisions are made during meetings by vote. \\
	The decisions are noted by the meeting secretary and shared after the meeting to all involved.
\end{itemize}

\section*{Log}
	To log our progress during this project we will create a blog which all can write in and must be updated at least once a week.


\section*{Documentation and file management}
\begin{itemize}
	\item Git, file management
	\item  LaTex, Reports and documentation
\end{itemize}

\section*{Ambition}
\begin{itemize}
	\item Develope software for motion capturing with Kinect. Capture and track arbitrary objects and process data in a efficient and effective way.
	\item Spread knowledge in the area of computer visualisation and get more people involved in the open source community.

\end{itemize}

\section*{Violation of contract}
	\begin{description}
	\item[First] \hfill \\
	Talk to whom ever it may concern.
	\item[Second] \hfill \\
	Discuss with the entire group to find a solution.
	\item[Third] \hfill \\
	Contact our mentor.
\end{description}


\begin{center}
\begin{tabular}{ p{7cm} p{7cm}}
	Signature & Date \\
	

\setlength{\unitlength}{5cm}
	\begin{picture}(1.5,0.4)
	\put(0,0){\line(1,0){1.3}}
	\end{picture} & 
\setlength{\unitlength}{5cm}
	\begin{picture}(1.5,0.4)
	\put(0,0){\line(1,0){0.6}}
	\end{picture} \\
	Jens Christensen \\
	
\setlength{\unitlength}{5cm}
	\begin{picture}(1.5,0.4)
	\put(0,0){\line(1,0){1.3}}
	\end{picture} & 
\setlength{\unitlength}{5cm}
	\begin{picture}(1.5,0.4)
	\put(0,0){\line(1,0){0.6}}
	\end{picture} \\
	Jonas Brandvik \\
	
\setlength{\unitlength}{5cm}
	\begin{picture}(1.5,0.4)
	\put(0,0){\line(1,0){1.3}}
	\end{picture} & 
\setlength{\unitlength}{5cm}
	\begin{picture}(1.5,0.4)
	\put(0,0){\line(1,0){0.6}}
	\end{picture} \\
	Oliver Carlsson \\
	
\setlength{\unitlength}{5cm}
	\begin{picture}(1.5,0.4)
	\put(0,0){\line(1,0){1.3}}
	\end{picture} & 
\setlength{\unitlength}{5cm}
	\begin{picture}(1.5,0.4)
	\put(0,0){\line(1,0){0.6}}
	\end{picture} \\
	Viktor Alexander Jakobsson \\


\end{tabular}
\end{center}




\end{document}

	
	